Towards Verifying the Bitcoin-S Library

### 2019-06-23 paper/paper.tex
changed transaction code to see actual transaction

  val signedTxF: Future[Transaction] = txBuilderF
    .flatMap(_.sign)                       // call sign on the transaction builder
    .map {
      (tx: Transaction) => println(tx.hex) // transaction in hex for the bitcoin network
    }
\end{lstlisting}

\todo{ramon: change code to get an actual transaction, completely understand and explain the code}

>>>>

  val txF: Future[Transaction] = txBuilderF.flatMap(_.sign)

  val tx: Transaction = Await.result(signedTxF, 1 second)
\end{lstlisting}

\todo{ramon: completely understand and explain the code}
